\LARGE \bf Simultaneous Hand-Eye and Robot-World Calibration by Solving the AX=YB Problem without Correspondence*

### 2015-11-22 DrC Version 1/root1.tex
Added new proof

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H).
\end{equation}
Defining the PDF %probability density function
of $\{A_i\}$ and $\{B_i\}$ as:
\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{A_{i}}(H) \IEEEyessubnumber
\\*
f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{B_{i}}(H), \IEEEyessubnumber
\end{IEEEeqnarray}
then by using the bi-linearity of convolution, add $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ7}), and substitute Eq.\textcolor{blue}{~}(\ref{equ8}) into the summation, and we will have:
\begin{equation}\label{equ9}
(f_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B_{i}})(H).
\end{equation}

@@

\begin{IEEEeqnarray}{l}
M_{A} X = Y M_{B} \IEEEyessubnumber\label{equ15a}
\\*
Ad(X^{-1})\Sigma_{A}Ad^{T}(X^{-1}) = \Sigma_{B}. \IEEEyessubnumber\label{equ15b}
\end{IEEEeqnarray}
This is a nonparametric result, meaning that the underlying probability density functions $f_A(H)$
and $f_B(H)$ need not be Gaussian or belong to any other family of parametric distributions.
Moreover, the constraint of being highly-focused is not very restrictive because the original
data sets $\{A_i\}$ and $\{B_i\}$ can always be transformed into $\{(A_i)^p\}$ and $\{(B_i)^p\}$
for some fractional power $0 < p < 1$ since
$$ A_i = X B_i X^{-1} \,\, \Longleftrightarrow \,\, (A_i)^p = X (B_i)^p X^{-1}. $$
{\color{blue} Question: this is for AX=XB, but for AX =YB, $A_i = Y B_i X^{-1}$ and the above equation doesn't apply.}

The smaller the value of $p$ is, the more concentrated the transformed data will be.

>>>>

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H).
\end{equation}
Defining the PDF %probability density function
of $\{A_i\}$ and $\{B_i\}$ as:
\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{A_{i}}(H) \IEEEyessubnumber
\\*
f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta_{B_{i}}(H), \IEEEyessubnumber
\end{IEEEeqnarray}
then by using the bi-linearity of convolution, add $n$ instances of Eq.\textcolor{blue}{~}(\ref{equ7}), and substitute Eq.\textcolor{blue}{~}(\ref{equ8}) into the summation, and we will have:
\begin{equation}\label{equ9}
(f_{A}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B})(H).
\end{equation}

@@

\begin{IEEEeqnarray}{l}
M_{A} X = Y M_{B} \IEEEyessubnumber\label{equ15a}
\\*
Ad(X^{-1})\Sigma_{A}Ad^{T}(X^{-1}) = \Sigma_{B}. \IEEEyessubnumber\label{equ15b}
\end{IEEEeqnarray}
This is a nonparametric result, meaning that the underlying probability density functions $f_A(H)$
and $f_B(H)$ need not be Gaussian or belong to any other family of parametric distributions.
Moreover, it can be shown as below that in the context of $AX=YB$, Eq.~(\ref{equ15a}) and Eq.~(\ref{equ15b}) don't require $f_A$ and $f_B$ to be highly concentrated.

Starting with Eq.(\ref{equ9}), performing a convolution on both of the left sides of the equation with
$\delta_{Y^{-1}}(H)$, and using the associativity of convolution, we will have:
\begin{equation} 
(\delta_{Y^{-1}} * f_A * \delta_X)(H) = f_B(H).
\label{equ18new}
\end{equation}
Use the definition of mean as in Eq.~(\ref{equ11}) along with Eq.~(\ref{equ18new}), we have 
$$ \int_{SE(3)} \log({M}_{B}^{-1} H) f_B(H) dH = $$
$$ \int_{SE(3)} \log({M}_{B}^{-1} H) (\delta_{X^{-1}} * f_A * \delta_{X})(H) dH = $$
\begin{equation}
\int_{SE(3)} \log({M}_{B}^{-1} H) f_A({Y} H {X}^{-1}) dH = \mathbb{O}.
\label{equ19new}
\end{equation}
Change the variable as $K = {Y} H {X}^{-1}$ and use the invariance of integration \cite{chirikjian2011stochastic}, then Eq.~(\ref{equ19new}) becomes:
\begin{equation}
\int_{SE(3)} \log({M}_{B}^{-1} Y^{-1} K X) f_A(K) dK = \mathbb{O}. 
\label{equ20new}
\end{equation}
which falls into the form of the mean definition of $\{A_i\}$.
If we further multiply $X$ and $X^{-1}$ on the left and right of both sides of Eq.~(\ref{equ20new}), then $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(M_{A}^{-1}K)$.
Knowing that $X[\log({M}_{B}^{-1} Y^{-1} K X)]X^{-1} = \log(X {M}_{B}^{-1} Y^{-1} K)$, and we have 
$X {M}_{B}^{-1} Y^{-1} = M_{A}^{-1}$ which is equivalent to Eq.~(\ref{equ15a}),
